---
title: "ej_map"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

```{r}
library(sf)
library(tidyverse)

```


## EJ Map - ATSDR

Load geobase file

```{r}

ej_map <- st_read("G:/My Drive/Air Pollution EJ/GIS EJ/United states.gdb", layer = "eji_ranks") %>% 
  st_zm() %>% 
  as("Spatial")

ej_map %>% as_tibble()


```


From Data dictionary documentation:

2022 variables:

SPL_EJI: Summation of the HVM, EBI, and SVI module percentile ranks

*RPL_EJI: Percentile ranks of SPL_EJI*

SPL_SER: Summation of the EB, and SV module percentile ranks

RPL_SER: Percentile ranks of SPL_SER

EPL_OZONE: Percentile rank of annual mean days above O3 regulatory standard - 3-year average

EPL_PM: Percentile rank of annual mean days above PM2.5 regulatory standard - 3-year average

SPL_EBM_THEME1: Domain consisting of ozone, PM2.5, air toxics cancer risk, and diesel particulate matter.

*RPL_EBM_DOM1: Percentile rank of domain consisting of ozone, PM2.5, air toxics cancer risk, and diesel particulate matter.*

# https://r-spatial.github.io/sf/articles/sf5.html

```{r}
plot(ej_map, max_plot = 1)

plot(ej_map["SPL_EBM_THEME1"])

plot(ej_map$RPL_EJI)


```


